An efficient algorithm for integer lattice reduction

### 2023-08-22 tex/paper.tex
updating pseudocode

\LinesNumbered
\begin{algorithm}
\caption{Series of ten sequences, each having the same three steps:
(1) random permutation followed by
(2) the LLL algorithm of~\cite{lenstra-lenstra-lovasz} followed by
(3) Algorithm~\ref{ours}}
\label{combination}
\DontPrintSemicolon
\KwIn{A positive integer $n$, a positive real number $p$, and
column vectors $a^0_1$, $a^0_2$, \dots, $a^0_n$, each of size $n \times 1$.}
\KwOut{Column vectors $a^{10}_1$, $a^{10}_2$, \dots, $a^{10}_n$,
each $n \times 1$,
such that the vectors are a unimodular integer linear transformation
of the input vectors $a^0_1$, $a^0_2$, \dots, $a^0_n$.}

@@

Run the LLL algorithm of~\cite{lenstra-lenstra-lovasz}
(implemented as detailed in Subsection~\ref{implementation})
on $b^i_1$, $b^i_2$, \dots, $b^i_n$ to obtain
vectors $b^{i+1}_1$, $b^{i+1}_2$, \dots, $b^{i+1}_n$,
each $n \times 1$, such that $b^{i+1}_1$, $b^{i+1}_2$, \dots, $b^{i+1}_n$
are a unimodular integer linear transformation of the vectors
$b^i_1$, $b^i_2$, \dots, $b^i_n$.

>>>>

\LinesNumbered
\begin{algorithm}
\caption{Series of ten sequences, each having the same three steps:
(1) random permutation followed by
(2) the LLL algorithm of~\cite{lenstra-lenstra-lovasz} followed by
(3) Algorithm~\ref{ours}}
\label{combination}
\DontPrintSemicolon
\KwIn{A positive integer $n$, positive real numbers $p$ and $\delta$, and
column vectors $a^0_1$, $a^0_2$, \dots, $a^0_n$, each of size $n \times 1$.}
\KwOut{Column vectors $a^{10}_1$, $a^{10}_2$, \dots, $a^{10}_n$,
each $n \times 1$,
such that the vectors are a unimodular integer linear transformation
of the input vectors $a^0_1$, $a^0_2$, \dots, $a^0_n$.}

@@

Run the LLL algorithm of~\cite{lenstra-lenstra-lovasz}
(implemented as detailed in Subsection~\ref{implementation}, while using
the given value of the parameter $\delta$ for the Lov\'asz criterion)
on $b^i_1$, $b^i_2$, \dots, $b^i_n$ to obtain
vectors $b^{i+1}_1$, $b^{i+1}_2$, \dots, $b^{i+1}_n$,
each $n \times 1$, such that $b^{i+1}_1$, $b^{i+1}_2$, \dots, $b^{i+1}_n$
are a unimodular integer linear transformation of the vectors
$b^i_1$, $b^i_2$, \dots, $b^i_n$.
